Formal Synthesis of Digital Controllers for Observable Continuous Plants with Transient Performance Specifications

### 2017-10-13 TACAS2018/paper.tex
comments/edits sec 5

where $0\leq p_s \leq 1$ is the desired percentage of the target within to remain after $t_s$.

@@

In most real implementations, the internal state of a plant cannot be directly measured. All we can do is infer its
value through its effecton the output. A plant model that minimises the difference between the outputs is called
an observer and it is a well known paradigm in the control literature\cite{astrom1997computer}. Since we are
interested in synthesising controllers with observer designs, we need to look at the challenges presented by 
the introduction of the observer.

@@

As stated in Section~\ref{ssec:stabspecification}, we use Jury's Criterion
to assert this specification.

Now that we have established convergence, we may examine the safety
specification of the state space.  In the case of SISO systems, this is
given by a range of the input and a range of the output which are considered
safe ($\vec{u}_k \in [\underline{u}\ \ \overline{u}] \wedge \vec{y}_k \in
[\underline{y}\ \ \overline{y}]$).  Whilst there are other properties we may
include in the verification, we will solely focus on these for simplicity of
the explanation.  We will assume that we do not want saturation in our
system, hence the control loop has only one mode.  We have also identified
the quantization noise as a bounded non-deterministic input.  First we must
translate the safety specification into the statespace.  Replacing on the
second part of equation \eqref{eq:observer_LTI_cf} we obtain
%
\begin{equation}
\phi_{safety} := \underline{y}<\mat{C}\vec{x}_k<\overline{y}, \forall k \geq 0
\label{eq:of_bounds}
\end{equation}
%
%Note that we use the bounds of the input after the transformation by $\mat{B}$ since the matrix may reverse the bounds. 
%
Equation~\eqref{eq:of_bounds} can be solved using linear programming as it
describes a polyhedral region in $\mathbb{R}^p$.  The second step is
evaluating the progression of the system over time in order to calculate
$\vec{x}_k$ to validate against this specification.  For this step we require
an initial set from which the system progresses.  Obviously, this set
$\vec{x}_0$ must satisfy the specification, otherwise the system will be
unsafe to begin with.  We will accept a specification in the form
$\mat{E}\mat{T}\vec{x}_0<\mat{f}$.  The presence of $\mat{T}$ is because
this will typically be given in the original state-space.

@@

Thus far we have presented a verification procedure for a continuous plant
in discretized time domain (i.e., the range of the quatizers is still
$\mathbb{R}$).  The next step we must reaize is that the controller and the
observer exist in a digital program, hence their domain is
$\mathbb{R}_{\langle C \rangle}$.  This has two separate effects on the
model.  If we recall Equation~\eqref{eq:observer_LTI}, the matrices of the observer
and the controller are not necessarily those of the plant.  In fact we have
$\mat{A},\mat{B},\mat{C} \in \mathbb{R}^*$, ${\mat{A}_d}_{\langle C
\rangle},{\mat{B}_d}_{\langle C \rangle},{\mat{C}_d}_{\langle C \rangle},
\mat{K}_{\langle C \rangle}, \mat{L}_{\langle C \rangle} \in
\mathbb{R}_{\langle C \rangle}^*$ where $*$ represents the appropriate
dimension for each matrix.  Unfortunately this means that although combined
matrices such as $\mat{A}_t$ are in the reals, they suffer from the fixed
word restrictions in their composing matrices.

@@

>>>>

where $0\leq p_s \leq 1$ is the desired percentage of the target within \todo{typo?} to remain after $t_s$.

@@

In most real implementations, the internal state of a plant cannot be
directly measured but rather inferred from its
effect on the output. A plant model that minimises the difference
between the outputs is called an observer and it is a well known
paradigm in the control literature~\cite{astrom1997computer}. Since we
are interested in synthesising controllers with observer designs, in this
section we will look at checking stability and safety in the presence of an observer.

%the challenges presented by the introduction of the observer.

@@

As stated in Section~\ref{ssec:stabspecification}, we use Jury's Criterion
to assert this specification. \todo{Not clear to me what ``this specification'' refers to.}

@@

Thus far we looked at checking stability
%have presented a verification procedure for
of a continuous plant in discretized time domain (i.e., the range of the quatizers is still
$\mathbb{R}$) \todo{do you mean that we only considered time domains discretization until now and
now we look at value domain discretization as well?}.  The next step we must realize is that the controller and the
observer exist in a digital program, hence their domain is
$\mathbb{R}_{\langle C \rangle}$.  This has two separate effects on the
model.  If we recall Equation~\eqref{eq:observer_LTI}, the matrices of the observer
and the controller are not necessarily those of the plant.  In fact we have
$\mat{A},\mat{B},\mat{C} \in \mathbb{R}^*$, ${\mat{A}_d}_{\langle C
\rangle},{\mat{B}_d}_{\langle C \rangle},{\mat{C}_d}_{\langle C \rangle},
\mat{K}_{\langle C \rangle}, \mat{L}_{\langle C \rangle} \in
\mathbb{R}_{\langle C \rangle}^*$ where $*$ represents the appropriate
dimension for each matrix.  Unfortunately this means that although combined
matrices such as $\mat{A}_t$ are in the reals, they suffer from the fixed
word restrictions in their composing matrices.

@@

%% Now that we have established convergence, we may examine the safety
%% specification of the state space.
In the case of SISO systems, the safety specification is
given by a range of the input and a range of the output which are considered
safe ($\vec{u}_k \in [\underline{u}\ \ \overline{u}] \wedge \vec{y}_k \in
[\underline{y}\ \ \overline{y}]$)
\todo{I think the safety specification is generally on the states of the system.}.
Whilst there are other properties we may
include in the verification, we will solely focus on these for simplicity of
the explanation.  We assume that we do not want saturation in our
system, hence the control loop has only one mode.
%We have also identified the quantization noise as a bounded non-deterministic input.
First we must
translate the safety specification into the statespace.  Replacing on the
second part of equation \eqref{eq:observer_LTI_cf} we obtain
%
\begin{equation}
\phi_{safety} := \underline{y}<\mat{C}\vec{x}_k<\overline{y}, \forall k \geq 0
\label{eq:of_bounds}
\end{equation}
\todo{what happened to u when going from \eqref{eq:observer_LTI_cf}?}
%
%Note that we use the bounds of the input after the transformation by $\mat{B}$ since the matrix may reverse the bounds. 
%
\todo{I thought \eqref{eq:of_bounds} was the safety spec. Why is it solved?}
Equation~\eqref{eq:of_bounds} can be solved using linear programming as it
describes a polyhedral region in $\mathbb{R}^p$.  The second \todo{second?} step is
evaluating the progression of the system over time in order to calculate
$\vec{x}_k$ to validate against this specification.  For this step we require
an initial set $\vec{x}_0$ from which the system progresses.  Obviously, this set
%$\vec{x}_0$
must satisfy the specification, otherwise the system will be
unsafe to begin with.  We will accept a specification in the form
$\mat{E}\mat{T}\vec{x}_0<\mat{f}$ \todo{ET? f?}.  The presence of $\mat{T}$ is because
this will typically be given in the original state-space.
